### 2022-01-06 input/background.tex
starting with xas, small changes here and there
comment xas-cast

\item [Dynamic partitioning and adaptive scoped broadcast:]

Finally, in Figure~\ref{fig:partition_intuitionD}, \Process~$G$
destroys its replica. Every \process that belonged to its green
partition must choose another partition to be in. While it makes sense
for \Process~$G$ to scoped broadcast its removal, \Process~$B$ and
\Process~$R$ cannot afford to continuously advertise their replica to
fill the gap left open by \Process~$G$. Instead, we want to trigger
once again scoped broadcast at bordering \processes of red and blue
partitions. The scope of scoped broadcast changes over receipts by
\processes. Dynamic partitioning raises additional challenges related
to concurrent operations where removed partitions would block the
propagation of other partitions (see Section~\ref{subsec:dynamic}).
\end{asparadesc}

>>>>

\item [Dynamic partitioning:]

In Figure~\ref{fig:partition_intuitionD}, \Process $G$ destroys its
replica. Every \process that belonged to its green partition must
choose another partition to be in. While it makes sense for
\Process~$G$ to scoped broadcast its removal, \Process~$B$ and
\Process~$R$ cannot afford to continuously advertise their replica to
fill the gap left open by \Process~$G$. Instead, we want to trigger
once again scoped broadcast at bordering \processes of red and blue
partitions. The scope of scoped broadcast changes over receipts by
\processes. Dynamic partitioning raises additional challenges related
to concurrent operations where removed partitions would block the
propagation of other partitions (see Section~\ref{subsec:dynamic}).

%% \item [Lazy partitioning:]

%% \TODO{Finally, in Figure~\ref{fig:partition_intuition}, every nodes of
%%   the system maintains an index to every content. In systems
%%   comprising billions of content, this could constitute a scalability
%%   issue. The partitioning protocol should take advantage of boundary
%%   between autonomous systems in the Internet. For instance, the AS
%%   from France should not flood the AS from Spain unless the latter
%%   starts to host a replica. In addition, when the system removes its
%%   last source, it should stop receiving messages from other ASes
%%   designed to maintain the closest partition.}

\end{asparadesc}

### 2022-01-06 input/proposal.tex
comment xas-cast

To provide lazy and dynamic logical partitioning in dynamic networks
using scoped broadcast, all live \processes must collaborate to
disseminate messages that notify new or removed sources to all and
only interested \processes. This section reviews step-by-step the
properties that allow \processes to converge to the desired state
together. It first defines scoped broadcast, then uses it to guarantee
consistent partitioning when a \process can only become a new source
in the system. It highlights the issue when a \process can also remove
its status of source. It shows that using local knowledge and scoped
broadcast, \processes can still reach dynamic consistent partitioning
when they are able to detect possible blocking conditions in the
dissemination of required notifications. Finally, it further constrain
the system by allowing only subsets of \processes to reach lazy
consistent partitioning. This improvement only requires \processes to
know which of their neighbors belong to their own network.

@@

\subsection{Lazy dynamic consistent partitioning}
\label{subsec:lazy}

To further reduce the traffic generated by our DCP protocol, we
leverage that an Edge infrastructure is a network of autonomous
systems, only a small subset of which needs logical partitioning.

\begin{definition}[Edge infrastructure]
  An Edge infrastructure $\mathcal{G}$ has multiple autonomous systems
  interconnected with additional links $\mathcal{E} \in V_1 \times
  V_2$ where $V_1 \neq V_2$, hence $\mathcal{G} = \langle \{G_1,
  \ldots G_n\}, \mathcal{E} \rangle$. A \underline{g}ateway $g$ is a
  \process with at least one link towards another network: $\langle g,
  \_ \rangle \in \mathcal{E}$.
\end{definition}

At any time, an autonomous system start logical partitioning when a
\process from this network becomes a source.  Then every \process from
this network belongs to the partition of its closest source not only
from their own network but that of adjacent networks that started
logical partitioning as well.  At any time, an autonomous system stops
logical partitioning when the last source from this network revokes
its status of source. Eventually, all nodes from this network do not
belong to any partition and the generated traffic stops.

\begin{definition}[Lazy dynamic consistent partitioning (LDCP)]
  \TODO{If there exists at least a source in a network, its nodes must
    belong to the partition of the closest partition in adjacent
    networks. Otherwise, nodes must eventually belong to no
    partition.}
\end{definition}

To enable LDCP in an Edge infrastructure, we use the property provided
by DCP in an autonomous system to all its \processes and among others,
to its gateways.

\begin{lemma}[Source existence]
  When a system becomes quiescent, DCP guarantees that every \process
  eventually acknowledges the existence or non-existence of a source
  in its system.
\end{lemma}

\begin{proof}
  By design.
\end{proof}

The gateways become responsible for the flooding or the stopping of
notifications foreign to their respective network. They must
differentiate between local and global notifications. Local
notifications provide both \begin{inparaenum}[(i)]
\item local source existence, and
\item closest local source in the network
\end{inparaenum}; while global notifications only improve on closest global sources,
\ie it does not need to propagate when the foreign source is farther
than the local one.

\begin{definition}[\underline{B}roadcasting of \underline{u}ninterested (BU)]
  \TODO{meow}
\end{definition}

\TODO{Blocking condition local global remains.}

\TODO{Added invariant: global is always smaller than local when they
  exist.}

\begin{algorithm}[h]
  \input{input/algoxascast.tex}
  \caption{\label{algo:xascast}\NAMEC at \Process~$p$. \TODO{TODO.}}
\end{algorithm}

>>>>

To provide lazy and dynamic logical partitioning in dynamic networks
using scoped broadcast, all live \processes must collaborate to
disseminate messages that notify new or removed sources to all and
only interested \processes. This section reviews step-by-step the
properties that allow \processes to converge to the desired state
together. It first defines scoped broadcast, then uses it to guarantee
consistent partitioning when a \process can only become a new source
in the system. It highlights the issue when a \process can also remove
its status of source. It shows that using local knowledge and scoped
broadcast, \processes can still reach dynamic consistent partitioning
when they are able to detect possible blocking conditions in the
dissemination of required notifications. \TODO{Finally, it further constrain
the system by allowing only subsets of \processes to reach lazy
consistent partitioning. This improvement only requires \processes to
know which of their neighbors belong to their own network.}

@@

%% \subsection{Lazy dynamic consistent partitioning}
%% \label{subsec:lazy}

%% \input{input/figxasproblem.tex}

%% To further reduce the traffic generated by our DCP protocol, we
%% leverage that an Edge infrastructure is a \TODO{network of autonomous
%% systems}, only a small subset of which needs logical partitioning.

%% \begin{definition}[Edge infrastructure]
%%   An Edge infrastructure $\mathcal{G}$ has multiple autonomous systems
%%   interconnected with additional links $\mathcal{E} \in V_1 \times
%%   V_2$ where $V_1 \neq V_2$, hence $\mathcal{G} = \langle \{G_1,
%%   \ldots G_n\}, \mathcal{E} \rangle$. A \underline{g}ateway $g$ is a
%%   \process with at least one link towards another network: $\langle g,
%%   \_ \rangle \in \mathcal{E}$.
%% \end{definition}

%% At any time, an autonomous system start logical partitioning when a
%% \process from this network becomes a source.  Then every \process from
%% this network belongs to the partition of its closest source not only
%% from their own network but that of adjacent networks that started
%% logical partitioning as well.  At any time, an autonomous system stops
%% logical partitioning when the last source from this network revokes
%% its status of source. Eventually, all nodes from this network do not
%% belong to any partition and the generated traffic stops.

%% \begin{definition}[\TODO{Adjacent networks}]
%% \end{definition}

%% \begin{definition}[Lazy dynamic consistent partitioning (LDCP)]
%%   \TODO{If there exists at least a source in a network, its nodes must
%%     belong to the partition of the closest partition in adjacent
%%     networks. Otherwise, nodes must eventually belong to no
%%     partition.}
%% \end{definition}

%% \TODO{A naive implementation would consist in using gateways as
%%   additional gatekeepers of scoped broadcast. Figure that shows that
%%   it works mostly.}

%% \begin{lemma}[$\textup{FB}^+ \wedge \textup{FS}^+ \wedge \textup{G} \centernot\implies \textup{LDCP}$]
%%   \TODO{meow}
%% \end{lemma}

%% \begin{proof}
%%   \TODO{meow meow}
%% \end{proof}

%% \TODO{To enable LDCP in an Edge infrastructure, we use the property provided
%% by DCP in an autonomous system to all its \processes and among others,
%% to its gateways.}

%% \begin{lemma}[Source existence]
%%   When a system becomes quiescent, DCP guarantees that every \process
%%   eventually acknowledges the existence or non-existence of a source
%%   in its system.
%% \end{lemma}

%% \begin{proof}
%%   By design.
%% \end{proof}

%% The gateways become responsible for the flooding or the stopping of
%% notifications foreign to their respective network. They must
%% differentiate between local and global notifications. Local
%% notifications provide both \begin{inparaenum}[(i)]
%% \item local source existence, and
%% \item closest local source in the network
%% \end{inparaenum}; while global notifications only improve on closest global sources,
%% \ie it does not need to propagate when the foreign source is farther
%% than the local one.

%% \begin{definition}[\underline{B}roadcasting of \underline{u}ninterested (BU)]
%%   \TODO{meow}
%% \end{definition}

%% \TODO{Blocking condition local global remains.}

%% \TODO{Added invariant: global is always smaller than local when they
%%   exist.}

%% \begin{algorithm}[h]
%%   \input{input/algoxascast.tex}
%%   \caption{\label{algo:xascast}\NAMEC at \Process~$p$. \TODO{TODO.}}
%% \end{algorithm}

\TODO{Transition to experiments.}
